On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-01-20 TTau_Halpha/kurosawa.tex
Minor changes in the figure captions.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@625 25464f21-6099-402c-b30a-640f1d40d38b

  \caption{A comparison of the profiles computed with the magnetosphere,
    the wind, the disc, and their combinations. The model configurations 
    used above are: (1)~magnetosphere only (dash), (2)~wind and disc
    (dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
    used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
    $\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
    $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$,
    $T_{\mathrm{wind}}=8000\,\Kelvin$, and $\beta=0.5$. The profile for
    the case 3 is can be understood as a simple flux sum of the profiles
    from case 1 and 2.}

@@

  \caption{The effect of the mass-loss rate to mass-accretion rate ratio
    ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The H$\alpha$
    profile computed with only the magnetospheric accretion (thick
    solid) --- $T_{\mathrm{max}}=7500\,\Kelvin$,
    $\dot{M}_{acc}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ --- is compared with
    the magnetosphere, wind, and disc hybrid models for $\mu =$ 0.01
    (solid), 0.025 (dash-dot), 0.1 (dot) and 0.2 (dash). All the models
    are computed with the inclination angle $i=55^{\circ}$. As $\mu$
    increases the P-Cygni absorption deepens and the emission component
    becomes stronger. In general, the absorption is too strong for the
    models with $\mu>0.025$ compared to the observations (e.g.,
    \citealt{reipurth:1996}).}

>>>>

  \caption{A comparison of the profiles computed with the magnetosphere,
    the wind, the disc, and their combinations. The model configurations 
    used above are: (1)~magnetosphere only (dash), (2)~wind and disc
    (dot), and (3)~disc, wind and magnetosphere (solid).  The parameters
    used here are $T_{\mathrm{max}}=7500\,\Kelvin$,
    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$,
    $\dot{M}_{\mathrm{wind}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$,
    $T_{\mathrm{wind}}=9000\,\Kelvin$, and $\beta=0.5$. The profile for
    the case 3 is can be understood as a simple flux sum of the profiles
    from case 1 and 2.}

@@

  \caption{The effect of the mass-loss rate to mass-accretion rate
    ratio ($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$).  The
    H$\alpha$ profile computed with only the magnetospheric accretion
    (thick solid) is compared with the magnetosphere--wind--disc
    hybrid models for $\mu =$ 0.01 (solid), 0.025 (dash-dot), 0.1
    (dot) and 0.2 (dash). The magnetosphere used here has
    $T_{\mathrm{max}}=7500\,\Kelvin$ and
    $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$.  The
    temperature and the acceleration parameter of the bipolar wind are
    $T_{\mathrm{wind}}=7000\,\Kelvin$ and $\beta=2.0$ respectively.
    All the models are computed with the inclination angle
    $i=55^{\circ}$. As $\mu$ increases the P-Cygni absorption deepens
    and the emission component becomes stronger. In general, the
    absorption is too strong for the models with $\mu>0.025$ compared
    to the observations (e.g., \citealt{reipurth:1996}).}
